Model LF

### 2022-10-27 max_dp endogen stød.Rmd
Prøver at lave wage-led

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens3_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

@@

COMMENT> Er fixet
BEHAVIORAL> i_bd_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_bd_nfc_k_ds) = p_800 + 
p_801*TSDELTALOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_802*TSDELTALOG(ps_ds) + 
p_803*TSDELTALOG(u_ds) + 
p_804* LOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_805 * LOG(TSLAG(ps_ds,1)) + 
p_806 * LOG(TSLAG(u_ds,1)) + 
p_807 * TSDELTALOG(tobinq) +
p_808 * LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_bd_nfc_k_ds),1) + 
alpha_2*TSLAG(LOG(bd_nfc_k),1) + 
alpha_3*TSLAG(-LOG(bd_nfc_k),2)
COEFF> p_800 p_801 p_802 p_803 p_804 p_805 p_806 p_807 p_808 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(10)

@@

@@

  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens3_low = TIMESERIES(c(sens3_low),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

  i_bd_nfc_k_ds = TIMESERIES(c(i_bd_nfc_k_ds),   
                             START=c(2005,2),FREQ=4),

@@

#S_modelData$d_2007q4 = d_2007q4

@@

>>>>

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens3_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> Sensitivitets analyse
IDENTITY> disc
EQ> disc = disc*1

@@

COMMENT> Er fixet
BEHAVIORAL> i_bd_nfc_k_ds_used
TSRANGE 2006 1 2020 1
EQ> LOG(i_bd_nfc_k_ds_used) = p_800 + 
p_801*TSDELTALOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_802*TSDELTALOG(ps_ds) + 
p_803*TSDELTALOG(u_ds) + 
p_804* LOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_805 * LOG(TSLAG(ps_ds,1)) + 
p_806 * LOG(TSLAG(u_ds,1)) + 
p_807 * TSDELTALOG(tobinq) +
p_808 * LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_bd_nfc_k_ds),1) + 
alpha_2*TSLAG(LOG(bd_nfc_k),1) + 
alpha_3*TSLAG(-LOG(bd_nfc_k),2)
COEFF> p_800 p_801 p_802 p_803 p_804 p_805 p_806 p_807 p_808 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(10)

COMMENT> Er fixet
BEHAVIORAL> i_bd_nfc_k_ds_disc
TSRANGE 2006 1 2020 1
EQ> LOG(i_bd_nfc_k_ds_disc) = p_800 + 
p_801*TSDELTALOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_802*TSDELTALOG(ps_ds) + 
p_803*TSDELTALOG(u_ds) + 
p_804* LOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_805 * LOG(TSLAG(ps_ds,1)) + 
p_806 * LOG(TSLAG(u_ds,1)) + 
p_807 * TSDELTALOG(tobinq) +
p_808 * LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_bd_nfc_k_ds),1) + 
alpha_2*TSLAG(LOG(bd_nfc_k),1) + 
alpha_3*TSLAG(-LOG(bd_nfc_k),2)
COEFF> p_800 p_801 p_802 p_803 p_804 p_805 p_806 p_807 p_808 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
p_805 = 0.1
STORE> coe(50)

@@

COMMENT> 
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_used
if> disc <= 0
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_disc
if> disc > 0

@@

  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens3_low = TIMESERIES(c(sens3_low),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

  i_bd_nfc_k_ds = TIMESERIES(c(i_bd_nfc_k_ds),   
                             START=c(2005,2),FREQ=4),
  i_bd_nfc_k_ds_used = TIMESERIES(c(i_bd_nfc_k_ds),   
                             START=c(2005,2),FREQ=4),
  i_bd_nfc_k_ds_disc = TIMESERIES(c(i_bd_nfc_k_ds),   
                             START=c(2005,2),FREQ=4),

@@

S_modelData$disc = disc

@@

## Sens Disc

We change the estimate of ps_ds in i_bd_nfc_k_ds function to 0.1.

```{r}
# Define add-factor list (defining shock)
constantAdjList_disc <- list(

 disc = TIMESERIES(disc+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
disc_bs <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_disc
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_disc = disc_bs$simulation$max_dp
wage_disc = disc_bs$simulation$wage
komp_r_disc = disc_bs$simulation$komp_r
part_disc = disc_bs$simulation$part
yk_ds_disc = disc_bs$simulation$yk_ds
pc_ds_disc = disc_bs$simulation$pc_ds
wage_ds_t_disc = disc_bs$simulation$wage_ds_t
pc_ds_disc = disc_bs$simulation$pc_ds
max_gap_disc = disc_bs$simulation$max_gap
wage_gap1_disc = disc_bs$simulation$wage_gap1
inflation_disc = disc_bs$simulation$inflation
wage_ds_disc = disc_bs$simulation$wage_ds
emp_disc = disc_bs$simulation$emp
pconk_ds_disc = disc_bs$simulation$pconk_ds
nl_g_disc = disc_bs$simulation$nl_g
prod_disc = disc_bs$simulation$prod

ik_disc = disc_bs$simulation$ik
```

```{r}
# Define add-factor list (defining shock)
constantAdjList1_disc <- list(

 disc = TIMESERIES(disc+1 ,START=c(2006,3),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)
```

```{r}
# Simulate the model (following shock)
disc_S1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_disc
                    )
```

```{r}
max_dp_disc_01 = disc_S1$simulation$max_dp
wage_disc_01 = disc_S1$simulation$wage
komp_r_disc_01 = disc_S1$simulation$komp_r
part_disc_01 = disc_S1$simulation$part
yk_ds_disc_01 = disc_S1$simulation$yk_ds
pc_ds_disc_01 = disc_S1$simulation$pc_ds
wage_ds_t_disc_01 = disc_S1$simulation$wage_ds_t
pc_ds_disc_01 = disc_S1$simulation$pc_ds
max_gap_disc_01 = disc_S1$simulation$max_gap
wage_ds_disc_01 = disc_S1$simulation$wage_ds
wage_gap1_disc_01 = disc_S1$simulation$wage_gap1
wage_gap_disc_01 = disc_S1$simulation$wage_gap
inflation_disc_01 = disc_S1$simulation$inflation
emp_disc_01 = disc_S1$simulation$emp
nl_g_disc_01 = disc_S1$simulation$nl_g
prod_disc_01 = disc_S1$simulation$prod
pconk_ds_disc_01 = disc_S1$simulation$pconk_ds

ik_disc_01 = disc_S1$simulation$ik
```

plot(((pconk_ds_disc_01 - pconk_ds_disc) / pconk_ds_disc_01), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_disc_01 - ik_disc) / ik_disc), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

```{r}
plot(((yk_ds_disc_01 - yk_ds_disc) / yk_ds_disc), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

```{r}
plot(((yk_ds_02 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");

grid()
```
